---
title: "Proposal"
author: "Jiazhang Cai"
date: "4/5/2020"
output: pdf_document
---

```{r warning=FALSE, include=FALSE}
library(tidyverse)
library(readr)
```

# Dataset     

The data is about the NFL stadium attendence from "https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-02-04". There are three tables in the dataset. The first one is the overview of the attendence:   


```{r echo=FALSE, warning=FALSE}
attendance <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/attendance.csv') %>%
  as.data.frame()
head(attendance)
```

the dictionary of this dataset is:    

variable | class | description
--------|--------|------------
team | character | team city
team_name | character | team name
year | integer | season year
total | double | total attendence across 17 weeks (1 week = no game)
home | double | total home attendence 
away | double | total away attendence
week | character | week number (1-17)
weekly_attendence | double | weekly attendence     

The second one is the information about each team:   

```{r echo=FALSE, warning=FALSE}
standings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/standings.csv') %>%
  as.data.frame()
head(standings)
```

the dictionary of this dataset is: 

variable | class | description
--------|--------|-------------
team | character | team city
team_name | character | team name
year | integer | season year
wins | double | wins (0-16)
loss | double | losses (0-16)
points_for | double | points for offensive performance
points_against | double | points for defensive performance
points_differential | double | points_for-points_against
margin_of schedule | double | (points scored-points allowed)/game played
strength_of_schedule | double | average quality of opponent as measured as measured by SRS
simple rating | double | team quality relative to average as measured by SRS
offensive_ranking | double | team offense quality relative to average as measured by SRS
defensive_ranking | double | team defense quality relative to average as measured by SRS
playoffs | character | made playoffs or not
sb_winner | character | won superbowl or not    

The last one is the information of every games:      

```{r echo=FALSE, warning=FALSE}
games <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-04/games.csv') %>%
  as.data.frame()
head(games)
```

the dictionary of this dataset is: 

variable | class | description
--------|--------|-------------
year | integer | season year
week | character | week number (1-17 and playoffs)
home_team | character | home team
away_team | character | away team
winner | character | winning team
tie | character | same for both team
day | character | day of week
date | character | date without year
time | character | time of game start
pts_win | double | points by winning team
pts_loss | double | points by lossing team
yds_win | double | yards by winning team
turnovers_win | double | turnovers by winning team
yds_loss | double | yards by losing team
turnovers_loss | double | turnovers by losing team
home_team_name | character | home team name
home_team_city | character | home team city
away_team_name | character | away team name
away_team_name | character | away team city

The additional data is from "https://www2.census.gov/programs-surveys/popest/datasets/2010-2019/national/totals/", the *United States Census* website. The data is about the population and population change in every state of the United States.    

# Plan    

The data I found have three aspects: the attendence, the teams and the games. The describe of this dataset is aiming to study the attendence performance. However, I think we can expand the thought because of the abundance of the information we have.    

First, we can study the attendence performance with the time, the location, the team played and something like that as the description of the dataset. To study deeper of the information about the location, I also find the data of population and population change in every state. In this part, I plan to get a map of the performance of the attendence in each state and maybe a model of predicting the attendence as well.    

Second, we can study the team strength with the performance of each team in all the games, like the points they got, the yards they ran and maybe there history performance. I hope the output is a model of estimating the strength using score like the quality measured by SRS (Simple Rating System) or maybe a model of predicting if the team will win the super bowl or make the playoffs, which may use the logistic model.    

Finally, we can also study the result of the games. There should be more effects to the result of the game excpet the strength of the teams. The time, the location, the attendence all could influnce the performance of the team. In this part, the ideal output is to get a model to predict the result of the game using all the information we have.    

It's important that the three parts study are independent with each other. For example, in the study of the team strength, we assume the strength is the response and the results of the games are parts of the effects. However, in the study of the games result, we assume the result is the response and the strength of team are parts of the effects. So we must be aware that we can't use the conclusion beyond the study we forcus on.      

# Presentation

It would be a systematic study, so I prefer a longer report instead of the presentation.  

Thank you!   













